---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

__Note__: This R package is not mean to be "serious". It's my submission for HW07 for STAT547.

# biof

This is an R package that gives `canonical()` and `complementary()` for getting the canonical and complementary DNA or RNA sequence respectively.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("STAT545-UBC-students/hw07-emreerhan")

# you'll also need:
install.packages('stringr')
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
biof::canonical('ACGT', minimal = FALSE)
biof::complementary('AUG', dna = FALSE)
```

## For Developers

You can build more small-scale sequence analysis utilities. For example, `get_kmers()` to kmerize a sequence.
